Policy Gradient Estimation

### 2019-03-07 pge-mattis.tex
Fix some misunderstandings

\paragraph{Definitions.} 
We define states $s \in \mathbb{S}$, actions $a \in \mathbb{A}$, and rewards $r \in \mathbb{R}$. 
For discrete problems, we assume $\mathbb{S} \equiv \{0,1,2,\ldots\}$ and $\mathbb{A} \equiv \{0,1,2,\ldots\}$ without loss of generality.
A trajectory $\tau_{\pi_\theta}^h := (s_0, a_0, $ $s_1, a_1, \dots, s_h, a_h)$ is generated by drawing $s_0 \sim p(x_0)$ according to the distribution over initial states $p(s_0)$, and successively sampling $a_t \sim \pi_\theta(a_t|s_t)$ according to the policy $\pi_\theta$, and $s_{t+1} \sim p(s_{t+1}|s_t,a_t)$ until the horizon $h$ is reached. 
At each time step, we receive a reward according to $r_t = r(s_t, a_t, s_{t+1})$. 
A trajectory can also be called \textit{roll-out} or \textit{episode}, though the term episode implies it ends in a terminal state.

We assume a Markov Decision Process (MDP), meaning the probability distribution of the next states is independent of past states $s_{0:t-1}$ given the present state $s_t$ and action $a_t$, 
\begin{equation}
	p(s_{t+1}|s_t,a_t)=p(s_{t+1}|s_{0:t},a_{0:t}).
\end{equation}
Where we define $i:j$ with $i,j \in \mathbb{N}, i < j$ as an index over all integers from $i$ to $j$, i.e., $s_{i:j} := s_i, s_{i+1}, \dots, s_j$.

@@

Since we have only limited knowledge of the performance of the policy, we need to approximate an optimal policy by estimating a gradient. 
Thus, we search $\nabla_\theta J(\theta) := \nabla_\theta \mathbb{E}_{p(\tau)}\left[\mathcal{R}^\tau\right]$, to make a policy gradient step according to $\theta_{k+1} = \theta_k + \alpha_k \nabla_\theta J(\theta)$, where $\alpha_k$ denotes a learning rate. 
It is shown that for $\lim_{k\to\infty}\alpha_k = 0$, and $\sum_{k=0}^\infty \alpha_k$ we are guaranteed to converge to a local optimum \cite{Sutton:1999:PGM:3009657.3009806}.

@@

\paragraph{Likelihood-ratio gradients.} 
For this derivation, we will change the perspective a bit requiring some additional definitions. 
We define ${\mu_\pi}_i = \sum_{t=0}^{\infty} p(s_t=s_i | s_0, \pi)$ \cite{puterman2014markov} as the state distribution, though it does not sum up to one without normalization. Note that $\mu_\pi$ is equivalent to the discounted state visit count $d^\pi$ introduced by Sutton et al. \cite{Sutton:1999:PGM:3009657.3009806}.
We define $P_\pi$ as the transition matrix, i.e. ${P_\pi}_{i,j}=p(s_j|s_i,\pi)$.
$r_\pi$ contains the mean rewards for all states given by ${r_\pi}_i = \int_\mathbb{A} r(s_i,a)\pi_\theta(a|s_i) da$. 
$\mu_0$ is the initial state distribution.
From which it follows that $V_\pi = \mu_\pi r_\pi$
From this, we derive
\begin{align}
	\mu_\pi &= \mu_0 + P_\pi^T \mu_\pi \nonumber \\
	(I-P^T)\mu_\pi &= \mu_0 \nonumber \\
	\mu_\pi^T &= \mu_0^T (I-P_\pi)^{-1} ,
\end{align}
so we can reformulate the problem as 
\begin{align}
	\underset{\theta}{\text{max}}\ J(\theta) &= \mu_0^T V_\pi \\
	\text{s.t.}\ V_\pi &= r_\pi + \gamma P_\pi V_\pi . \nonumber
\end{align}
Where $V_\pi = \left[ V_\pi(s_0), V_\pi(s_1), \ldots \right]^T$. We derive 
\begin{align*}
	\nabla_\theta J(\theta) &= \nabla_\theta \mu_0^T V_\pi
	\\ &= \mu_0^T \nabla_\theta \gamma P_\pi V_\pi
	\\ &= \mu_0^T (I - \gamma P_\pi)^{-1} (\nabla_\theta r_\pi + \gamma (\nabla_\theta P_\pi) V_\pi)
	\\ &= \mu_\pi^T (\nabla_\theta r_\pi + \gamma (\nabla_\theta P_\pi) r_\pi)
	\\ &\equiv \sum\nolimits_i d^\pi(s_i) \nabla_\theta\pi(a|s_i) Q(s_i,a)
	\\ &= \sum\nolimits_i d^\pi(s_i) \pi(a|s_i) \nabla_\theta\log\pi(a|s_i) Q_\pi(s_i,a).
\end{align*}
Where we used $\nabla_\theta \pi_\theta(a|s) = \pi_\theta(a|s)\nabla_\theta\log\pi_\theta(a|s)$, obtained from the likelihood ratio, which gives us the likelihood-ratio gradient,
\begin{equation}
	\nabla_\theta J(\theta) = \mathbb{E}_{\pi}\left[\nabla_\theta{\log\pi_\theta(a|s)}Q_\pi(s,a)\right].
	\label{eqn:like-grad}
\end{equation}
intuitively meaning we should to increase the probability of actions that lead to higher Q-values.

Obviously, we do not have the true $Q_\pi(s,a)$, thus we need to approximate it by $\hat{Q}_\pi(s,a)$. 
We draw $a \sim \pi(a|s)$, starting in state $s_0 \sim p(s_0)$ and match a function estimator to our observations.
Approximating $Q_\pi(s,a)$ by an unbiased estimator $f_w(s_t, a_t) \equiv \hat{Q}_\pi(s_t, a_t)$, Sutton et al. \cite{Sutton:1999:PGM:3009657.3009806} show that using this function approximation we will converge to the same local optimum.
However, they also find this requires $\int_\mathbb{S}{\pi(s,a)f_w(s,a)da} = 0$ for each state. 
Given this assumption, the function estimator $f_w$ is limited to an advantage function
\begin{equation}
	A^{\pi}(s_t, a_t) := Q^{\pi}(s_t, a_t) - V^{\pi}(s_t)
	\label{eqn:adv}
\end{equation}
as in \cite{1993b}, which is mean-zero. We present the effect of this in greater detail in \ref{sec:ac}, but it does not critically affect the following findings.

\paragraph{Immediate updates.} 
The first class of algorithms developed to update a policy directly were REINFORCE \cite{Williams92simplestatistical} algorithms.
REINFORCE uses immediate updates with a baseline $b$ in its gradient steps:
\begin{equation}
  \psi_t \leftarrow r_t-b.
\end{equation}

Obviously, this does not involve temporal information, and is very biased.
To reduce the estimate's bias, we can do updates from completed roll-outs.

@@

Episodic REINFORCE \cite{Williams92simplestatistical}, the first approach to this concept performs roll-outs and takes only the final return:
\begin{equation}
  \nabla_\theta J(\theta) \approx \frac{1}{h} \sum_{t=0}^h \nabla_\theta\log\pi_\theta(s) Q(s_t,a_t).
\end{equation}
This is sometimes also called Monte-Carlo gradient estimation. 
However, taking this a step further, it should be possible to attribute the reward at each step to the respective action.

Given $r_t > 0, \forall t=0,\dots,h$, these approaches can only increase action probabilities. 
Obviously, we normalize to ensure $\forall s \in \mathbb{S}: \int_\mathbb{A}{\pi(a|s)da} = 1$. 
This means actions can only become less probable in relation to other actions. 
We find that this introduces a lot of variance when learning from samples \cite{Sutton:1999:PGM:3009657.3009806}. 
One approach to counter the variance is to introduce a baseline
\begin{equation}
  \psi_t \leftarrow \gamma^{t} (r_{t} - b(s_t))
\end{equation}
The baseline can represent any prior knowledge or assumption about states, e.g., their mean value. 
Though we find that there is a specific way to use this baseline which fits surprisingly well into this framework.

@@

Policy gradient methods can be described in terms of two main steps often called policy evaluation and policy improvement. 
For actor-critic approaches, we separate these steps from the actor component by implementing a critic. 
This means, the actor consists only of the policy, while the critic is focused on estimating a score for the actions taken. 
By that concept, observations of $s_t$ from the environment are given to the actor only to decide the next action, and to the critic only to improve its function estimation with the respective $r_t$. 
Figure \ref{fig:ac} shows the general structure of an actor-critic algorithm.

\paragraph{Actor.} 
TODO

\paragraph{Critic.} 
The critic estimates a value function as defined in \eqref{eqn:v}. 
\cite{Sutton:1999:PGM:3009657.3009806}, and \cite{Konda:2003:AA:942271.942292} find that the estimation $f_w^\pi(s,a) \approx Q^\pi(s,a)$ does not affect the unbiasedness of the gradient estimate under some restrictions. 
Specifically, this holds for $f_w^\pi(s,a) = {\nabla_\theta \log\pi(a|s)}^T w$, thus $f_w^\pi(s,a)$ being a linear function parameterized by the vector $w$. 
However, as we have seen in the last section, \ref{sec:pge}, this function estimator will have a mean of zero $\int_\mathbb{A} \nabla_\theta \pi(a|s)du $, thus it estimates an advantage function \ref{eqn:adv}. 
However, to estimate the advantage function, we require $V^\pi(s)$. 
We will show how this leads to a new problem but still, this insight guarantees that function approximation does not cause divergence, and really enables recent research in reinforcement learning for continuous control problems, e.g., in humanoid robotics.

Traditionally, the improvement is often done by Monte-Carlo sampling as in REINFORCE, or using temporal difference (TD) \cite{Sutton1988}, i.e., we use the temporal difference between the critic's estimations 
\begin{equation}
  r_t + \gamma \hat{V}^\pi(s_{t+1}) - \hat{V}^\pi(s_t).
\end{equation}

This is where we need to come back to the insight that from $f_w^\pi(s,a) = {\nabla_\theta \log\pi(a|s)}^T w$, it follows that $f_w^\pi(s,a)$ estimates the advantage function, so we are bootstrapping for $V^\pi(s,a)$. 
If we use temporal difference in this context, we run into a problem, as \eqref{eqn:adv} subtracts $\hat{V}^\pi(s_t)$, meaning we would only learn immediate rewards \cite{Peters_IICHR_2003}. 
This would render the process biased. 
Sutton et al. \cite{Sutton:1999:PGM:3009657.3009806} and Konda et al. \cite{NIPS1999_1786} suggest estimating an action value function as in \eqref{eqn:q}. 
We can approximate this $f_w^\pi$ by least-squares optimization over multiple $\hat{Q}^\pi(s,a)$ obtained from roll-outs. 
However, Peters et al. \cite{4863} find that this approximation is highly reliant on the distribution of the training data. 
This comes from the realization, that we use only a subspace of the actual action value function in $f_w^\pi$, which is only a state value function. 
One can compare this to approximating a parabola by a line, whereby the approximation changes wildly depending on which part of the parabola is in the training data. 
An approach to solve this bootstrapping problem is to rewrite the Bellman Equation using \eqref{eqn:adv} and \eqref{eqn:q} with $A^\pi(s,a) = f_w^\pi(s,a)$, $V^\pi(s) = \phi(s)^T v$, and a zero-mean error term $\epsilon(s_t,a_t,s_{t+1})$, we get
\begin{align}
  Q^\pi(s,a) = A^\pi(s,a) + V^\pi(s) = r(s,a) + \gamma \int_\mathbb{S} p(s'|s,a)V^\pi(s')ds' \\
  \nabla_\theta \log \pi(a_t|s_t)^T w + \phi(s_t)^T v = r(s_t,a_t) + \gamma \phi(s_{t+1})^T v + \epsilon(s_t,a_t,s_{t+1})
\end{align}
which gives involves only linear equations to solve. \cite{4863}

@@

Using the Fisher information matrix $F_\theta$, and the gradient estimate we discussed in section \ref{sec:pge} gives us the definition
\begin{equation}
  \widetilde{\nabla}_\theta J(\theta) := F^{-1}_\theta \nabla_\theta J(\theta)
  \label{eqn:nat-grad}
\end{equation}
of the natural gradient. 
The Fisher information matrix represents the certainty we have on our estimate of the gradient and is defined as the covariance of the log likelihood function of a trajectory $\tau_{\pi_\theta}^h$, which as \cite{4863} show can be written as 
\begin{equation}
  F_\theta = \int_\mathbb{S} p(s|\theta) \int_\mathbb{A} \pi_\theta(a|s) \nabla_\theta \log{\pi_\theta(a|s)} \nabla_\theta \log{\pi_\theta(a|s)}^T dads.
  \label{eqn:F}
\end{equation}
When we recall the definition \eqref{eqn:like-grad} of likelihood-ratio gradients, we see that setting $\psi$ as $\nabla_\theta \log \pi(a|s)^T w$, we get
\begin{equation}
  \nabla_\theta J(\theta) = \int_\mathbb{S} {p(s|\theta) \int_\mathbb{A} \pi_\theta(a|s) \nabla_\theta \log \pi(a|s) {\nabla_\theta \log \pi(a|s)}^T dads}\ w := F_\theta w.
  \label{eqn:J-equals-F}
\end{equation}

@@

Note that this approach abuses some specific conveniences about the problem setup to find an elegant solution.
However, this is not the only way to approach this problem. 
In this paper, we focus on one presentation to present the core idea, but the field of policy gradient optimization is very resourceful. 
TODO 
In the conclusion \ref{sec:outro}, we attempt to show the versatility and relevance in current research, and give some directions for further reading.

>>>>

\paragraph{Definitions.} 
We define states $s \in \mathbb{S}$, actions $a \in \mathbb{A}$, and rewards $r \in \mathbb{R}$. 
A trajectory $\tau := (s_0, a_0, $ $s_1, a_1, \dots, s_h, a_h)$ is generated by drawing $s_0 \sim \mu_0(s_0)$ according to the distribution over initial states $\mu_0(s_0)$, and successively sampling $a_t \sim \pi_\theta(a_t|s_t)$ according to the policy $\pi_\theta$, and $s_{t+1} \sim p(s_{t+1}|s_t,a_t)$ until the horizon $h$, or a terminal state is reached. 
At each time step, we receive a reward according to $r_t = r(s_t, a_t) \equiv \mathbb{E}_{s'}\left[r(s_t,a_t,s')\right]$. 
A trajectory can also be called roll-out or episode, though the term episode implies it ends in a terminal state.
We assume a Markov Decision Process (MDP), meaning the probability distribution of the next states is independent of past states $s_{0:t-1}$ given the present state $s_t$ and action $a_t$, 
\begin{equation}
	p(s_{t+1}|s_t,a_t)=p(s_{t+1}|s_{0:t},a_{0:t}).
\end{equation}
Where we define $i:j$ with $i,j \in \mathbb{N}, i < j$ as an index over all integers from $i$ to $j$, i.e., $s_{i:j} \equiv s_i, s_{i+1}, \dots, s_j$. 
We assume no additional prior knowledge about the environment, thus we assume the probability of a trajectory is 
\begin{equation}
	p(\tau) = \mu_0(s_0) \prod_{t=0}^{h-1} p(s_{t+1}|s_{t}, a_{t}) \pi(a_t|s_{t}).
\end{equation}

@@

Since we have only limited knowledge of the performance of the policy, we need to approximate an optimal policy by estimating a gradient. 
Thus, we search $\nabla_\theta J(\theta) := \nabla_\theta \mathbb{E}_{p(\tau)}\left[\mathcal{R}^\tau\right]$, to make a policy gradient step according to $\theta_{k+1} = \theta_k + \alpha_k \nabla_\theta J(\theta)$, where $\alpha_k$ denotes a learning rate.

@@

\paragraph{Likelihood-ratio gradients.} 
For this derivation, we will change the perspective a bit requiring some additional definitions. 
We define ${\mu_\pi}_i = \sum_{t=0}^{\infty} p(s_t=s_i | s_0, \pi)$ \cite{puterman2014markov} as the state distribution, though it does not sum up to one without normalization. Note that $\mu_\pi$ is equivalent to the discounted state visit count $d^\pi$ introduced by Sutton et al. \cite{Sutton:1999:PGM:3009657.3009806}.
Further, we define $P_\pi$ as the transition matrix, i.e. ${P_\pi}_{i,j}=p(s_j|s_i,\pi)$, $r_\pi$ as the mean rewards for all states given by ${r_\pi}_i = \int_\mathbb{A} r(s_i,a)\pi_\theta(a|s_i) da$, and $\mu_0 = \left[\mu_0(s_0),\mu_0(s_1),\ldots\right]^T$ as a vector representing the initial state distribution.
From which it follows that $V_\pi = \mu_\pi r_\pi$
From this, we derive
\begin{align}
	\mu_\pi &= \mu_0 + P_\pi^T \mu_\pi \nonumber \\
	(I-P^T)\mu_\pi &= \mu_0 \nonumber \\
	\mu_\pi^T &= \mu_0^T (I-P_\pi)^{-1} ,
\end{align}
so we can reformulate the problem as 
\begin{align}
	\underset{\theta}{\text{max}}\ J(\theta) &= \mu_0^T V_\pi \\
	\text{s.t.}\ V_\pi &= r_\pi + \gamma P_\pi V_\pi . \nonumber
\end{align}
Where $V_\pi = \left[ V_\pi(s_0), V_\pi(s_1), \ldots \right]^T$. We derive 
\begin{align*}
	\nabla_\theta J(\theta) &= \nabla_\theta \mu_0^T V_\pi
	\\ &= \mu_0^T \nabla_\theta \gamma P_\pi V_\pi
	\\ &= \mu_0^T (I - \gamma P_\pi)^{-1} (\nabla_\theta r_\pi + \gamma (\nabla_\theta P_\pi) V_\pi)
	\\ &= \mu_\pi^T (\nabla_\theta r_\pi + \gamma (\nabla_\theta P_\pi) r_\pi)
	\\ &\equiv \sum\nolimits_i d^\pi(s_i) \nabla_\theta\pi(a|s_i) Q(s_i,a)
	\\ &= \sum\nolimits_i d^\pi(s_i) \pi(a|s_i) \nabla_\theta\log\pi(a|s_i) Q_\pi(s_i,a).
\end{align*}
Where we used $\nabla_\theta \pi_\theta(a|s) = \pi_\theta(a|s)\nabla_\theta\log\pi_\theta(a|s)$, obtained from the likelihood ratio, which gives us the likelihood-ratio gradient,
\begin{equation}
	\nabla_\theta J(\theta) = \mathbb{E}_{\pi}\left[\nabla_\theta{\log\pi_\theta(a|s)}Q_\pi(s,a)\right].
	\label{eqn:like-grad}
\end{equation}
intuitively meaning we should to increase the probability of actions that lead to higher Q-values.

Obviously, we do not have the true $Q_\pi(s,a)$, thus we need to approximate it by $\hat{Q}_\pi(s,a)$. 
We draw $a \sim \pi(a|s)$, starting in state $s_0 \sim p(s_0)$ and match a function estimator to our observations.
It is shown that for $\lim_{k\to\infty}\alpha_k = 0$, and $\sum_{k=0}^\infty \alpha_k$ we are guaranteed to converge to a local optimum \cite{Sutton:1999:PGM:3009657.3009806}.
Approximating $Q_\pi(s,a)$ by an unbiased estimator $f_w(s_t, a_t) \equiv \hat{Q}_\pi(s_t, a_t)$, Sutton et al. \cite{Sutton:1999:PGM:3009657.3009806} show that using this function approximation we will converge to the real local optimum.

\paragraph{Immediate updates.} 
The first class of algorithms developed to update a policy directly are called REINFORCE \cite{Williams92simplestatistical}.
REINFORCE collects a complete episode, at which point we can calculate the actual state-action value by traversing backwards over the trajectory, and estimates:
\begin{equation}
	\nabla_\theta J(\theta) \approx \nabla_\theta\log\pi_\theta(s) \left(Q(s_t,a_t) - b \right),
	\label{eqn:reinforce}
\end{equation}
where $b$ is some baseline. 
Peters \& Schaal \cite{4867} find that an estimate of the optimal baseline can be calculated by
\begin{equation}
	b = \frac
		{\left\langle 
			\left(\sum_{t=0}^h \nabla_\theta \log\pi_\theta(a_t|s_t) \right)^2 \sum_{l=0}^h a_l r_l 
		\right\rangle}
		{\left\langle
			\left(\sum_{t=0}^h \nabla_\theta \log\pi_\theta(a_t|s_t) \right)^2
		\right\rangle}
\end{equation}

However, this estimate is very biased.
To reduce the estimate's bias, we can compute updates from a complete episode.

@@

Episodic REINFORCE \cite{Williams92simplestatistical}, the first approach to this concept, performs roll-outs and takes the final return, at which point we can calculate the actual state-action value by traversing backwards over the trajectory, and estimates
\begin{equation}
  \nabla_\theta J(\theta) \approx \frac{1}{h} \sum_{t=0}^h \nabla_\theta\log\pi_\theta(s) Q(s_t,a_t).
\end{equation}
This is sometimes also called Monte-Carlo gradient estimation. 
Given $r_t > 0, \forall t=0,\dots,h$, these approaches can only increase action probabilities. 
Obviously, we normalize to ensure $\forall s \in \mathbb{S}: \int_\mathbb{A}{\pi(a|s)da} = 1$. 
This means actions can only become less probable in relation to other actions. 
We find that this introduces more variance when learning from samples \cite{Sutton:1999:PGM:3009657.3009806}. 
One approach to counter the variance is to introduce a baseline
\begin{equation}
  \hat{Q}(s,a) \approx \gamma^{t} (r_{t} - b(s_t)).
\end{equation}
The baseline can represent any prior knowledge or assumption about states. 
A common way to use this baseline is to use the value function, which gives us the so-called advantage function

\begin{equation}
	A_{\pi}(s_t, a_t) := Q_{\pi}(s_t, a_t) - V_{\pi}(s_t).
	\label{eqn:adv}
\end{equation}

@@

Policy gradient methods can be described in terms of two main steps often called policy evaluation and policy improvement. 
For actor-critic approaches, we separate these steps from the actor component by implementing a critic. 
This means, the actor consists only of the policy, while the critic is focused on estimating a score for the actions taken. 
By that concept, observations of the environment are given to the actor only to decide the next action, and to the critic only to improve its function estimation with the respective rewards. 
Figure \ref{fig:ac} shows the general structure of an actor-critic algorithm.

The critic estimates a state-action value function as defined in \eqref{eqn:q}. 
\cite{Sutton:1999:PGM:3009657.3009806}, and \cite{Konda:2003:AA:942271.942292} find that the estimation $f_w^\pi(s,a) \approx Q_\pi(s,a)$ does not affect the unbiasedness of the gradient estimate under some restrictions. 
Specifically, this holds for $f_w^\pi(s,a) = {\nabla_\theta \log\pi(a|s)}^T w$, thus $f_w^\pi(s,a)$ being a linear function parameterized by the vector $w$.
This guarantees that the function estimator does not cause divergence, and really enables recent research in reinforcement learning for continuous control problems, e.g., in humanoid robotics.

Traditionally, the improvement is often done by Monte-Carlo sampling as in REINFORCE \eqref{eqn:reinforce}, or using temporal difference (TD) \cite{Sutton1988}, i.e., we use the temporal difference between the critic's estimations 
\begin{equation}
  r_t + \gamma \hat{V}_\pi(s_{t+1}) - \hat{V}_\pi(s_t).
\end{equation}

However, Sutton et al. \cite{1993b} find that this is only guaranteed to be unbiased, if $\int_\mathbb{S}{\pi(s,a)f_w(s,a)da} = 0$ for each state. 
Given this assumption, the function estimator $f_w$ is limited to an advantage function \eqref{eqn:adv}, which requires bootstrapping for $V_\pi(s,a)$. 
If we use temporal difference in this context, we run into a problem, as \eqref{eqn:adv} subtracts $\hat{V}_\pi(s_t)$, meaning we would only learn immediate rewards \cite{Peters_IICHR_2003}. 
This would render the process biased. 
Sutton et al. \cite{Sutton:1999:PGM:3009657.3009806} and Konda et al. \cite{NIPS1999_1786} suggest estimating an action value function as in \eqref{eqn:q}. 
We can approximate this $f_w^\pi$ by least-squares optimization over multiple $\hat{Q}_\pi(s,a)$ obtained from roll-outs. 
However, Peters et al. \cite{4863} find that this approximation is highly reliant on the distribution of the training data. 
This comes from the realization, that we use only a subspace of the actual action value function in $f_w^\pi$, which is only a state value function. 
One can compare this to approximating a parabola by a line, whereby the approximation changes wildly depending on which part of the parabola is in the training data. 
An approach to solve this bootstrapping problem is to rewrite the Bellman Equation using \eqref{eqn:adv} and \eqref{eqn:q} with $A_\pi(s,a) = f_w^\pi(s,a)$, $V_\pi(s) = \phi(s)^T v$, and a zero-mean error term $\epsilon(s_t,a_t,s_{t+1})$, we get
\begin{align}
  Q_\pi(s,a) = A_\pi(s,a) + V_\pi(s) &= r(s,a) + \gamma \int_\mathbb{S} p(s'|s,a)V_\pi(s')ds' \\
  \nabla_\theta \log \pi(a_t|s_t)^T w + \phi(s_t)^T v &= r(s_t,a_t) + \gamma \phi(s_{t+1})^T v + \epsilon(s_t,a_t,s_{t+1})
\end{align}
which gives involves only linear equations to solve. \cite{4863}

@@

Using the Fisher information matrix $F_\theta$, and the gradient estimate we discussed in section \ref{sec:pge} gives us the definition
\begin{equation}
  \widetilde{\nabla}_\theta J(\theta) := F^{-1}_\theta \nabla_\theta J(\theta)
  \label{eqn:nat-grad}
\end{equation}
of the natural gradient. 
The Fisher information matrix represents the certainty we have on our estimate of the gradient and is defined as the covariance of the log likelihood function of a trajectory $\tau_{\pi_\theta}^h$, which as \cite{4863} show can be written as 
\begin{equation}
  F_\theta = \int_\mathbb{S} d^\pi(s) \int_\mathbb{A} \pi_\theta(a|s) \nabla_\theta \log{\pi_\theta(a|s)} \nabla_\theta \log{\pi_\theta(a|s)}^T dads.
  \label{eqn:F}
\end{equation}
When we recall the definition \eqref{eqn:like-grad} of likelihood-ratio gradients, we see that setting $\hat{Q}(s,a) := \nabla_\theta \log \pi(a|s)^T w$, we get
\begin{equation}
  \nabla_\theta J(\theta) = \int_\mathbb{S} {p(s|\theta) \int_\mathbb{A} \pi_\theta(a|s) \nabla_\theta \log \pi(a|s) {\nabla_\theta \log \pi(a|s)}^T dads}\ w \equiv F_\theta w.
  \label{eqn:J-equals-F}
\end{equation}

@@

However, the natural gradient is similarly used by TODO: reference other algos using natural gradient and remove them from conclusion (TRPO?)

In the conclusion \ref{sec:outro}, we attempt to show the versatility and relevance in current research, and give some directions for further reading.
